Argennon: A Scalable Cloud Based Smart Contract Platform Using Argument of Knowledge Systems

### 2022-08-20 tex/sections/intro.tex
Fix readability issues
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The most common use for blockchains is in financial applications. This gives a crucial importance to the
security of the consensus protocol used in a blockchain. Unfortunately, many currently used blockchains are
vulnerable to a certain type of consensus attack, known as the bribery attack. In a bribery attack, an adversary
tries to corrupt participants of a protocol by offering them money and making them violate the protocol.

At the time of writing of this document,
the total mining reward for a bitcoin block is around \$150,000. If we assume, in decision theoretic terminology,
that the mining reward accurately defines the utility function of a bitcoin miner, one could hire all hashing power
of the bitcoin network for one hour by
spending only \$750,000. The situation is not much different for PoS blockchains, as long as the total
stake of the validator set is a relatively small value. Here by
stake, we mean a real number measuring the total interest of a user in the system. We are not referring, in
particular, to some locked amount of a user's money that is known as stake in some PoS protocols.

This problem is more severe in blockchains that use randomly selected small sets of validators. These small sets
usually have low total stake and could be easily bribed and corrupted. Selecting these random sets
by hidden random procedures would not help, since the validator himself knows he has been selected, before casting
his vote.

@@

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. The consensus protocol of a blockchain relies on a network of computers, not humans. Ordinary users
use simple and similar computer systems. That means, they all have similar vulnerabilities and weaknesses which could be
used by an adversary to catastrophically attack the consensus protocol. For instance, if a malware, probably using a
common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, it could be used by an
adversary to control the majority of participants in the consensus protocol and compromise the security of the
blockchain.

Securing a computer system against cyberattacks needs planning ahead and access to engineering resources.
Special software and hardware, like custom-built operating systems and isolated specialized hardware is required.
This is not something a normal user can afford. Only powerful centralized entities having large financial and
technical resources, could build
systems that are resilient against sophisticated cyberattacks. In this regard, we have to admit, a centralized system is
arguably superior to a decentralized\footnote{Note that decentralized and distributed are two different concepts.}
system.

@@

In case the main committee fails to generate new blocks or behaves maliciously, a special Recovery Protocol is
initiated by validators.
This recovery protocol can recover the functionality
of the Argennon blockchain as long as more than $2/3$ of the total stake of the system is controlled by honest users
and any network partition resolves after a finite amount of time. The Recovery Protocol uses two main emergency
procedures to recover the functionality of the Argennon blockchain: \emph{emergency forking} and \emph{emergency
agreement} protocol.

@@

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different CI statements are independent of each other and can be done in parallel. As a result, a validator can use
multiple cores for verifying CI statements of a \textbf{single} block and different validator assemblies can
simultaneously and
independently verify \textbf{different} blocks.
In addition, proof generation of different CI statements similarly can be done in parallel. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing external requests and
generating the state transition as fast as possible.

@@

Using succinct argument of knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. In addition, this contract will facilitate
trustless bridging of assets to the Argennon blockchain. To reduce the execution fee, this validator
contract could be used for validating only roll-ups of state transition.

>>>>

The most common use for blockchains is in financial applications. This gives a crucial importance to the
security of the consensus protocol used in a blockchain. Unfortunately, many currently used blockchains are
vulnerable to a certain type of consensus attack, known as the Bribery Attack. In a Bribery Attack, an adversary
tries to corrupt participants of a protocol by offering them money and seducing them to violate the protocol.

At the time of writing of this document,
the total mining reward for a Bitcoin block is around \$150,000. If we assume, in decision theoretic terminology,
that the mining reward accurately defines the utility function of a Bitcoin miner, one could hire all hashing power
of the Bitcoin network for one hour by
spending only \$750,000. The situation is not much different for PoS blockchains, as long as the total
stake of the validator set is a relatively small value. By
stake, we mean a real number measuring the total interest of a user in the system, and we are not referring, in
particular, to some locked amount of a user's money that is known as stake in some PoS protocols.
This problem is more severe in blockchains that use randomly selected small sets of validators. These small sets
usually have low total stake and could be easily bribed and corrupted. Selecting these random sets
by hidden random procedures would not help, since the validator himself knows he has been selected, before casting
his vote.

@@

Although a fully decentralized blockchain based on the participation of every user looks appealing, it is not as perfect
as it might seem. The consensus protocol of a blockchain relies on a network of computers, not humans. Ordinary users
use simple and similar computer systems. That means, they all have similar vulnerabilities and weaknesses which could be
used by an adversary to catastrophically attack the consensus protocol. For instance, if a malware, probably using a
common zero-day
vulnerability, has the ability to infect a large portion of normal personal computers, an adversary can use it to
take control of the majority of participants in the consensus protocol and compromise the security of the
blockchain.

Securing a computer system against cyberattacks needs planning ahead and access to engineering resources.
Special software and hardware, like custom-built operating systems and isolated specialized hardware are required.
This is not something a normal user can afford. But powerful centralized entities, having large financial and
technical resources, could actually build
systems that are resilient against sophisticated cyberattacks. In this regard, we have to admit, a centralized system is
arguably superior to a decentralized\footnote{Note that decentralized and distributed are two different concepts.}
system.

@@

In case the main committee fails to generate new blocks or behaves maliciously, a special Recovery Protocol is
initiated by validators.
This recovery protocol can recover the functionality
of the Argennon blockchain as long as more than $2/3$ of the total stake of the system is controlled by honest users
and any network partition resolves after a finite amount of time. The Recovery Protocol uses two main emergency
procedures to recover the functionality of the Argennon blockchain: \emph{Emergency Forking} and \emph{Emergency
Agreement} protocol.

@@

Verifying a succinct proof can be exponentially faster than replaying the computation. Moreover, verifications of
different CI statements are independent of each other and can be done in parallel. As a result, a validator can use
multiple cores for verifying CI statements of a \textbf{single block} and different validator assemblies can
simultaneously and
independently verify \textbf{different blocks}.
In addition, proof generation of different CI statements similarly can be done in parallel. However, for parallel
proof generation, the state transition needs to be known in advance. That's why in Argennon, delegates do not try
to generate proofs and focus all their computational power on executing external requests and
generating the state transition as fast as possible.

@@

Using Succinct Argument of Knowledge systems makes the main functionalities of an Argennon validator light enough to
be implemented as a smart contract. By deploying a validator contract on another platform, Argennon
could use more established blockchains as an extra layer of security, specially
during the bootstrapping phase, when ARG is not well distributed yet. In addition, this contract will facilitate
trustless bridging of assets to the Argennon blockchain. To reduce the execution fee, this validator
contract can be used for validating only roll-ups of the state transition.
